clusters

### 2015-07-10 cluster.rmd
cluster refine

clust.km<- cascadeKM(clust %>% select(inv.mlsto, balance.mlsto, return.pdol,
                                      suc, hrs.mlsto), 2, 15, iter= 100)
plot(clust.km, sortg = TRUE, grpmts.plot = TRUE)

@@

rect.hclust(fit, k=11, border='red')

@@

k1<- kmeans(clust %>% select(inv.mlsto, balance.mlsto, return.pdol, suc, hrs.mlsto), 11)

@@

# add medians
all7c.med<- ddply(kmeans.plot, .(groups), numcolwise(median))

@@

@@

>>>>

clust.km<- cascadeKM(clust %>% select(inv.mlsto,suc), 2, 20, iter= 100)
plot(clust.km, sortg = TRUE, grpmts.plot = TRUE)

@@

rect.hclust(fit, k=15, border='red')

@@

k1<- kmeans(clust %>% select(inv.mlsto, balance.mlsto, return.pdol, suc, hrs.mlsto), 15)

@@

# add medians
all7c.med<- ddply(kmeans.plot, .(groups), numcolwise(median)) %>% round(2)

@@

#investigate clusters
all7c %>% filter(groups == 5) %>% select(inv.mlsto, suc, pc.majpos, majority.pos,
                                         code.client, client.meaninv, code.director, code.ProjEng,
                                         return.pdol, balance.mlsto, Year, timespan, pc.pro,
                                         pc.director, JD.Second, Business, client.count, Discipline,
                                         code.client, Billing.Type) %>% summary

@@

Visualise confidence intervals in terms of 'success'

```{r CI, echo=FALSE}
library('RcmdrPlugin.BCA',lib='C:/Progra~1/R/R-3.2.1/library')
# principal component analysis
#convert cluster groups to integer

all7c$groups<- as.integer(all7c$groups)
p<- prcomp(~suc+ inv.mlsto + balance.mlsto + cost.mlsto + return.pdol, data=all7c, centre=T)
# summary(p)
biplot(p, xlabs = as.character(all7c$groups))
#putlers in-house biplot shows centroids
bpCent(p, clsAsgn = all7c$groups, centroids=TRUE, xlabs = as.character(all7c$groups))

#now look at 3D - triplot - using prcomp
#scores stored as 'x' variable
p$x
plot3d(p$x[,1:3], col=as.character(all7c$groups))
text3d(p$x[,1:3], texts = as.character(all7c$groups), color=as.character(all7c$groups), adj=2)
text3d(p$rotation[,1:3], text = rownames(p$rotation), color= 'red')
coords <- NULL
for (i in 1:nrow(p$rotation)) {
        coords <- rbind(coords, rbind(c(0,0,0), p$rotation[i,1:3]))
}
lines3d(coords, col="red", lwd=4)
